Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2022-12-01 paper/paper1/ms.tex
Some figures and text around the 2D heatmap scans

\subsection{Calcium IR Triplet and other line diagnostics}
We examined the Calcium IR Triplet lines (Ca IRT) for evidence of variability.  No variation was seen in these features, which were pre-processed in the same way as the Helium feature.  Figure \ref{x} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at

>>>>

\subsection{Calcium IR Triplet and other line diagnostics}
We examined the Calcium IR Triplet lines (Ca IRT) for evidence of variability.  No variation was seen in these features, which were pre-processed in the same way as the Helium feature.  Figure \ref{fig:CaPhaseScan} shows a similar phase plot as Figure \ref{fig:HPFscanResid}, adapted to the line at 8662 $\AA$.  We see no conspicuous variability at this or any of the other Ca IRT lines.  We also found no detectable variability in the Pa$\delta$ line at 10050 $\AA$, nor other deep lines at 10330 $\AA$ and elsewhere.  Helium 10830 appears to be the only conspicuously variable line in the HPF spectrum.

\begin{figure}
    \includegraphics[width=\linewidth]{figures/Ca8662_phase_2D_diagram_resid.png}
    \caption{Non-detection of variability in the Calcium IR Triplet line at 8862 $\AA$.  No other HPF lines appear to show any variability.}
    \label{fig:CaPhaseScan}
\end{figure}

\subsection{Velocity substructure}
Figure \ref{fig:HeliumScanZoom} shows a zoom-in of the in-transit portion of the absorption residual scan.  The scan exhibits some velocity substructure.  At transit ingress, the absorption

\begin{figure}
    \includegraphics[width=\linewidth]{figures/phase_2D_diagram_zoom.png}
    \caption{A zoom-in of the in-transit and post-transit phase scan for the Helium 10830 triplet.  Some velocity substructure may be seen.}
    \label{fig:HeliumScanZoom}
\end{figure}
